Verifying Demonstrations

### 2018-05-31 paper/DB-anon-cred.tex

\ProvideDocumentCommand{\DBPK}{o o}{\ensuremath{%
    \operatorname{DBPK}%
    \IfValueT{#1}{%
      \IfValueTF{#2}{%
        \mleft\{\mleft(#1\mright) : #2\mright\}%
      }{%
        \mleft\{#1\mright\}%
      }%
    }%
  }}

One protocol exists in the literature providing \ac{DBPK} with all the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of Knowledge, instead of \ac{DBPK}.}.
However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie protocols of the form \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{DBPK} protocol for discrete logarithms (\ie \(\DBPK[\alpha][a = g^\alpha]\)).
To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.

>>>>

\ProvideDocumentCommand{\PPK}{o o}{\ensuremath{%
    \operatorname{PPK}%
    \IfValueT{#1}{%
      \IfValueTF{#2}{%
        \mleft\{\mleft(#1\mright) : #2\mright\}%
      }{%
        \mleft\{#1\mright\}%
      }%
    }%
  }}

One protocol exists in the literature that provides \acp{PPK} with all the 
desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
  shorter notation.}.
However, ProProx provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.
